{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-30 brains-protocol.tex
Update Fig. 4 caption

All in all, apart for Word frequency and despite some tendencies these results do not allow us to conclude either to an effect or no effect of the selected psycholinguistic features on substitution susceptibility.
We may therefore globally assume that substitution targets are chosen in a more or less uniform way with respect to these features.

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_susceptibilities.png}
    \caption{\textbf{Substitution susceptibility:} average susceptibility to substitution vs. average feature value of a candidate word for substitution, with 95\% asymptotic confidence intervals.
    Each feature exhibits a specific and significant pattern favoring either high- or low-valued words for substitution.}
    \label{fig:feature-susceptibilities}
\end{figure*}

>>>>

All in all, apart from Word frequency and despite some tendencies these results do not allow us to conclude either to an effect or to no effect of the selected psycholinguistic features on substitution susceptibility.
We may therefore globally assume that substitution targets are chosen in a more or less uniform way with respect to these features.

@@

\begin{figure*}[!th]
    \centering
    \includegraphics[width=\textwidth]{images/computed-figures/feature_susceptibilities.png}
    \caption{\textbf{Substitution susceptibility:} average susceptibility to substitution vs. average feature value of a candidate word for substitution, with 95\% asymptotic confidence intervals.
    \TB{Apart from Word frequency (where low-frequency words are more susceptible than high-frequency words), results do not let us conclude either to an effect or to no effect of the features on susceptibility.
    The heatmap on the lower-right, detailing the interaction of Age of acquisition and Number of phonemes on susceptibility, also shows no significant effect once outlier values are discarded.}}
    \label{fig:feature-susceptibilities}
\end{figure*}
